#### Compare a variable to a list of values
* find if a vlaue exists in a vector:
```{r}

vec1 <- c(1,2,3,"abc","hab",123)
x <- 2
print(is.element(x,vec1))
[1] TRUE

x <- 4
print(is.element(x,vec1))
[1] FALSE

x <- c("abc",4)
print(is.element(x,vec1))
[1]  TRUE FALSE
```


#### Subseting specific list of columns from a data frame
* subset()
```{r}
df <- read.csv("file.csv")
colnames(df)
[1] "c1" "c2" "c3" "c4" "c5"

sub_df <- subset(
                  df,c1 == "abc" & !is.na(complete.cases(df[c2]),
                    select =c("c1","c2","c4"))
# this command will return specific columns of the df dataframe based on some conditions
# first the value in c1 should be equal to "abc"
# second the value in c2 should not be NA .. c2 should have value.
# if both conditions match then return the columns specified in the select statemnet 
# if select not used will return all columns

```
#### Changing the names of a specific column/list of columns/all columns
```{r}
colnames(dataframe)[2] <- "column 3"
colnames(dataframe)[c(1,3,5)] <- c("Col 1","Col 3","Col 5")
colnames(dataframe)<-c("c1","c2","c3","c4","c5")
```
#### Stop the warning message temporarly during the coercion process to avoid NA warnings 

* there are two options:
* option (1)
```{r}
#disable the warning message temporarly
options(warn = -1)
outcome_file[,outcome] <- as.numeric(outcome_file[,outcome])
# enabling the warning messages again
options(warn = 0)
```
* option (2)
```{r}
suppressWarnings(outcome_file[,outcome] <- as.numeric(outcome_file[,outcome]))
```
#### Appending to a vector
#### loading a Vector into a Matrix by row.
#### invisible

